A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-09 main.tex
transition variable

The subscription $\alpha$ is a transition variable which is called a stage variable in \LMD.
It is used to show the thickness of quoting.
For example, $\TB_\alpha (\lambda x:\I.x+10)$ is a fragment of code which becomes $(\lambda x:\I.x+10)$ after run it once and
$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after run it twice.
\red{run twiceは表現が微妙}

@@

>>>>

The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable}.
It is used to show the thickness of brackets.
For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after it was run it twice.
\red{run twiceは表現が微妙}

@@

\red{, which is called a \textit{stage variable} in \LMD.}
